Haskell in Computational Biology

### 2013-05-06 jfp.tex
A note trying to make the lazy search stuff more explicit.

\noindent
\vbox{
Using these pieces, function \texttt{everyPt} produces an infinite
sequence containing a mix of useful and useless moves:
\smallfuzzverbatiminput{10.8pt}{everygen}
}
\noindent
Both \texttt{nextPt} and \texttt{utility} are monadic, but 
we can still exploit laziness:
from its starting point, \texttt{everyPt} produces an infinite list of
randomly chosen successor points, then calls \texttt{costedUtility} to
tag each one with a cumulative cost and a utility.
We~hope that if you look carefully at how \texttt{successors} is computed,
you will understand why we
separate \texttt{pt0}~from~\texttt{nextPt} instead of using a single
function that produces an infinite list:
We~don't \emph{want} the infinite list that would result from
applying \texttt{nextPt} to many points in succession;
we~want the infinite list that results from applying \texttt{nextPt}
to \texttt{startPt} many times in succession, each time with a
different source of randomness.

>>>>

\noindent
\vbox{
Using these pieces, function \texttt{everyPt} produces an infinite
sequence containing a mix of useful and useless moves:
\smallfuzzverbatiminput{10.8pt}{everygen}
}
\noindent
Both \texttt{nextPt} and \texttt{utility} are monadic, but 
we can still exploit laziness:
from its starting point, \texttt{everyPt} produces an infinite list of
randomly chosen successor points, then calls \texttt{costedUtility} to
tag each one with a cumulative cost and a utility.

In Hughes's \citeyearpar{hughes:why} classic model of lazy search,
we~might expect to use an infinite sequence of points obtained by
applying \texttt{nextPt} to many points in succession, as done by
the Prelude function \texttt{iterate}.
But~if you look carefully at how \texttt{successors} is computed,
that's not what's happening:
instead, we~compute an infinite list by applying \texttt{nextPt} to
a~\emph{single} initial point using infinitely many distinct sources
of random variation.
Then, when we find a useful \texttt{newPt}, a~recursive call
to \texttt{everyPt} computes a \emph{fresh} infinite sequence of
single jumps starting at~\texttt{newPt}.
\mrfy's search may explore an arbitrary number of infinite
lists of points, and the representation we~found easiest to think
about is the pair of elements
\texttt{pt0}~and~\texttt{nextPt} in the \texttt{SearchGen} record.
